Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-05-20 document/ms.tex
definition of gamma earth in introduction and summary in intro

@@

\section{Validation using synthetic catalogs}

@@

>>>>

Conditioned on our assumptions and the choices made in planet detection,
vetting and characterization pipeline (\citealt{petigura-a, petigura}), we
constrain the rate of small exoplanets orbiting Sun-like stars.
As part of this analysis we also place probabilistic constraints on the rate
of Earth analogs \gammaearth\ which we define as \emph{the number density of
planets per natural logarithmic bin in period and radius evaluated at the
location of Earth}
\begin{eqnarray}
\gammaearth &=&
\left.\frac{\dd N}{\dd\ln\period\,\dd\ln\radius}\right|
_{\radius=\radius_\oplus,\,\period=\period_\oplus}\quad.
\end{eqnarray}
Since no Earth analogs have been detected, this constraint requires an
extrapolation in both period and radius.
\citet{petigura} performed this extrapolation by assuming that the period
distribution of planets in a small bin in radius is flat and extrapolated from
their sample.
We relax this assumption and extrapolate by only assuming that the
occurrence rate function is ``smooth'' in period and radius.
We enforce this constraint by applying a flexible Gaussian process
regularization to the bin heights.

In the next section, we introduce the concept of hierarchical inference, how
it applies to the problem at hand, and we derive the importance sampling
approximation to the marginalized likelihood (this is a generalization of the
method from \citealt{hogge}).
Then, in \sect{model}, we describe how to include detection efficiencies in
this model and derive a probabilistic motivation for the standard
inverse-detection-efficiency weighting procedure.
After testing our method on synthetic catalogs in \sect{valid}, we use the
catalog of planet candidates and the empirically determined detection
efficiency from \citet{petigura} to measure the occurrence rate of Earth
analogs.

@@

\section{Validation using synthetic catalogs}
\sectlabel{valid}

@@

Our constraints are less confident---in a signal-to-noise sense---than
previous measurements (made using stronger assumptions; \citealt{petigura})
but, even so, our result is
